Additional analysis

### 2018-06-25 03_additional-analysis.Rmd
Ha, load magrittr

# Load libraries again
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(glue)
library(ggstance)
library(ggridges)
library(grid)
library(Gmisc)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(here)

>>>>

# Load libraries again
library(tidyverse)
library(magrittr)
library(rstanarm)
library(broom)
library(coda)
library(glue)
library(ggstance)
library(ggridges)
library(grid)
library(Gmisc)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(here)
